notes

### 2022-08-29 analysis/paper/gp-to-review-and-delete/notes.Rmd
add badges and binder

I moved the leftover codes from paper, just in case I need them later.

@@

```{R}

@@

@@

>>>>

I moved the leftover codes from paper, just in case I need them later. 
```{r}
#box plot for CV for each attributes
box2 <- boxplot(cvmap) ##Is there any better way to show this data??
```

cv_plot_site %>%
  pivot_longer(cols = -sitename, 
               names_to = "group") %>%
  ggplot(aes(x = sitename, 
             y = value, 
             fill = as.factor(group))) +
  geom_bar(stat = "identity", 
           position = position_dodge())

@@

```{r}
### three phases at once
library(patchwork)
call + ctwo + cthree + plot_layout(ncol=1)

direction_all+ direction_2 + direction_3 + plot_layout(ncol=1)

```{r}
xx_pca1_2 <- 
  data.frame(xx_pca2$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage ==2]))

ggplot(xx_pca1_2 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

xx_pca1_3 <- 
  data.frame(xx_pca3$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage ==3]))

ggplot(xx_pca1_3 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

Contribution of variables for each of four PCA dimensions of ALL phases except for the first.

```{r}
library(gridExtra)
library(factoextra)
PC1_v <- fviz_contrib(xx_pca, choice = "var", axes = 1, top = 7)
PC2_v <- fviz_contrib(xx_pca, choice = "var", axes = 2, top = 7)
PC3_v <- fviz_contrib(xx_pca, choice = "var", axes = 3, top = 7)
PC4_v <- fviz_contrib(xx_pca, choice = "var", axes = 4, top = 7)

grid.arrange(PC1_v, PC2_v, PC3_v, PC4_v, nrow =2)

@@

correlate(SYG6_DF) %>% 
  network_plot()

@@

correlate(SYG1_2DF) %>% 
  network_plot()

correlate(SYG1_1DF) %>% 
  network_plot()
